Mbh-n paper

### 2015-10-21 papers/mbhn/mbhn.tex
wed

\section{Introduction}
The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 
yet its physical origin has remained unexplained for decades. 
The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that
\begin{equation}
I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
\end{equation}
where $I_{\rm e}$ indicates the intensity at the effective radius $R_{\rm e}$ that encloses half of the total light from the model, 
the S\'ersic index $n$ is the parameter that regulates the curvature of the radial light profile, 
and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
A large S\'ersic index corresponds to a steep central profile and a shallow outer profile, 
whereas a small S\'ersic index corresponds to a shallow central profile and a steep outer profile. 
This means that, for a stellar spheroidal system whose light distribution is well approximated by the S\'ersic model, 
the larger the S\'ersic index $n$ is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
A compelling physical interpretation for the S\'ersic profile family was recently theorized by \cite{cen2014} 
and later confirmed by \cite{nipoti2015} by means of $N$-body simulations. 
\cite{cen2014} conjectured that, when structures form within a standard cold dark matter model seeded by random Gaussian fluctuations, 
any centrally concentrated stellar structure always possesses an extended stellar envelope, and vice versa. 
\cite{nipoti2015} quantitatively explored Cen's hypothesis and showed that 
systems originated from several mergers have a large S\'ersic index ($n \gtrsim 4$), 
whereas systems with a S\'ersic index as small as $n \simeq 2$ can be produced by coherent dissipationless collapse, 
and exponential profiles ($n=1$) can only be obtained through dissipative processes.
This scenario sets the theoretical framework for the well known correlation between the spheroid luminosity, $L_{\rm sph}$,  
and the spheroid S\'ersic index, $n_{\rm sph}$, (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}), 
although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with $n$ as large as $7 - 10$, 
which are commonly observed in the local Universe.  \\
Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
and the relation between the central black hole mass, $M_{\rm BH}$, and $L_{\rm sph}$ (e.g.~\citealt{magorrian1998}), 
an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
(measured through a parameter different from but closely related to the S\'ersic index), 
\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation.

s+11 v+12 b+12  \\
my paper \\
paper I and II \\

\section{Data}

@@

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}

>>>>

\section{Introduction}
The empirical \cite{sersic1963,sersic1968} $R^{1/n}$ model has been demonstrated to provide adequate description 
of the light distribution of the stellar spheroidal and disk components of galaxies (add REFS), 
yet its physical origin has remained unexplained for decades. 
The S\'ersic model parametrizes the intensity $I$ as a function of the projected galactic radius $R$ such that
\begin{equation}
I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 
\end{equation}
where $I_{\rm e}$ indicates the intensity at the effective radius $R_{\rm e}$ that encloses half of the total light from the model, 
the S\'ersic index $n$ is the parameter that regulates the curvature of the radial light profile, 
and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 
A large S\'ersic index corresponds to a steep inner profile and a shallow outer profile, 
whereas a small S\'ersic index corresponds to a shallow inner profile and a steep outer profile. 
This means that, for a stellar spheroidal system whose light distribution is well approximated by the S\'ersic model, 
the larger the S\'ersic index is, the more centrally concentrated the stars are and the more extended the outer envelope is. \\
A compelling physical interpretation for the S\'ersic profile family was recently theorized by \cite{cen2014} 
and later confirmed by \cite{nipoti2015} by means of $N$-body simulations. 
\cite{cen2014} conjectured that, when structures form within a standard cold dark matter model seeded by random Gaussian fluctuations, 
any centrally concentrated stellar structure always possesses an extended stellar envelope, and vice versa. 
\cite{nipoti2015} quantitatively explored Cen's hypothesis and showed that 
systems originated from several mergers have a large S\'ersic index ($n \gtrsim 4$), 
whereas systems with a S\'ersic index as small as $n \simeq 2$ can be produced by coherent dissipationless collapse, 
and exponential profiles ($n=1$) can only be obtained through dissipative processes.
This scenario sets the theoretical framework for the well known correlation between the spheroid luminosity, $L_{\rm sph}$,  
and the spheroid S\'ersic index, $n_{\rm sph}$, (e.g.~\citealt{youngcurrie1994,jerjen2000,grahamguzman2003}), 
although the numerical results of \cite{nipoti2015} seem to lack of spheroidal systems with S\'ersic indices as large as $7 - 10$, 
which are commonly observed in the local Universe.  \\
Given the existence of the $L_{\rm sph} - n_{\rm sph}$ correlation 
and the relation between the central black hole mass, $M_{\rm BH}$, and the spheroid luminosity (e.g.~\citealt{magorrian1998}), 
an $M_{\rm BH} - n_{\rm sph}$ relation must exist. 
After \cite{graham2001} showed that the black hole mass is tightly linked to the stellar light concentration of spheroids 
(measured through a parameter different from, but closely related to the S\'ersic index), 
\cite{grahamdriver2007} presented for the first time the $M_{\rm BH} - n_{\rm sph}$ correlation 
using a sample of 27 elliptical and disk galaxies. 
\cite{grahamdriver2007} fit their data with a log-quadratic regression, 
finding that the $M_{\rm BH} - n_{\rm sph}$ log-relation is steeper for spheroids with small S\'ersic indices 
and shallower for spheroids with large S\'ersic indices, 
and measured a relatively small level of scatter\footnote{At the time, the $M_{\rm BH} - \sigma$ relation 
\citep{ferraresemerritt2000,gebhardt2000} was reported to have the same level of scatter as the $M_{\rm BH} - n_{\rm sph}$ 
relation ($\simeq 0.3~\rm dex$). }.
A few years later, \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} performed multi-component decompositions 
for samples of galaxies similar to that used by \cite{grahamdriver2007}, 
but they surprisingly failed to recover a strong $M_{\rm BH} - n_{\rm sph}$ relation. 
This issue was tackled by \cite{savorgnan2013}, who collected the S\'ersic index measurements published by 
\cite{grahamdriver2007}, \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} for a sample of 54 galaxies, 
and showed that, by rejecting the most discrepant measurements and averaging the remaning ones, 
a strong $M_{\rm BH} - n_{\rm sph}$ relation was retrieved. 
Remarkably, \cite{savorgnan2013} repeated their analysis upon excluding the S\'ersic index measurements of \cite{grahamdriver2007} 
and still regained a significant $M_{\rm BH} - n_{\rm sph}$ relation. 
This was suggestive that the individual galaxy decompositions of \cite{sani2011}, \cite{vika2012} and \cite{beifiori2012} were not accurate, 
i.e.~each individual study obtained ``noisy'' S\'ersic index measurements 
which prevented the recovery of a strong $M_{\rm BH} - n_{\rm sph}$ relation. \\
Motivated by the need of more accurate galaxy decompositions to refine and re-investigate scaling relations 
between the black hole mass and several galaxy structural parameters, 
we performed state-of-the-art modelling for the largest sample of galaxies to date (Savorgnan \& Graham 2015, hereafter \emph{Paper I}),  
for which a dynamical measurement of the black hole mass was available.
In doing so, we used $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery, 
given its superb capability to trace the stellar mass (\citealt{sheth2010}, and references therein). 
In Savorgnan et al.~(2015, hereafter \emph{Paper II}) we examined the correlations between black hole mass and 
galaxy luminosity, spheroid luminosity and spheroid stellar mass. 
In this Paper (\emph{Paper III}) we focus on the $M_{\rm BH} - n_{\rm sph}$ relation. \\
This paper is structured as follows...

\section{Data}
We populated the $M_{\rm BH} - n_{\rm sph}$ diagram with the same galaxy sample used in \emph{Paper II}, 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii 
(see Savorgnan \& Graham 2015 for a discussion on this topic).

%%%
Spheroid magnitudes were derived from our state-ofthe-
art galaxy decompositions, which take into account
%%%
bulge, disks, spiral arms, bars, rings, halo, extended or
unresolved nuclear source and partially depleted core.
%%%
Kinematical information (Emsellem et al. 2011; Scott
et al. 2014; Arnold et al. 2014) was used to conrm the
%%%
presence of rotationally supported disk components in
most early-type (elliptical + lenticular) galaxies, and to
%%%
identify their extent (intermediate-scale disks that are
fully embedded in the bulge, or large-scale disks that encase
%%%
the bulge and dominate the light at large radii).
It is worth stressing that, contrary to common knowledge,
%%%
the majority of elliptical galaxies contain disks,
i.e. they are not single-component spheroidal systems.
%%%
Paper I presents the dataset used here, including details
about the data reduction process and the galaxy modelling
%%%
technique that we developed. It also discusses how
we estimated the uncertainties5 on the bulge magnitudes,
%%%and presents the individual 66 galaxy decompositions,
along with a comparison and discussion of past decompositions.
%%%The morphological classication (E = elliptical; E/S0 =
elliptical/lenticular; S0 = lenticular; S0/Sp = lenticular/
%%%
spiral; Sp = spiral; and merger") follows from the
galaxy models presented in Paper I. Throughout this paper
%%%
we will refer to early-type galaxies (E+S0) and latetype
galaxies (Sp). Two galaxies classied as E/S0 are
%%%
obviously included in the early-type bin, whereas two
galaxies classied as S0/Sp and another two classied as
%%%
mergers are included in neither the early- nor the latetype
bin.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_vs_n_maj.pdf}
\caption{}
\label{fig:magn}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_n_maj.pdf}
\caption{}
\label{fig:mbhn}
\end{center}
\end{figure}
